Comprehensive study of the global phase diagram of the $J$-$K$-$\Gamma$ model on a triangular lattice

### 2021-01-24 paper/paper.tex
Paper 2021-01-24 13:55

\documentclass[aps,prb,reprint,amsfonts,amsmath,amssymb,showpacs,groupedaddress,superscriptaddress]{revtex4-1}
\usepackage{bm}
\usepackage{color}
\usepackage{graphicx}
\usepackage[colorlinks,urlcolor=blue,linkcolor=blue,anchorcolor=blue,citecolor=blue,bookmarks]{hyperref}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{ModelDefinition.pdf}
    \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron. (b) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron. The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame. (c) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively. The different colors of the lattice sites label the four sublattices realizing the four sublattice transformation ( see main text for details).}
\end{figure}
In fact, magnetic ions located at the center of edge-sharing octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}. On the experimental side, studies on several classes of  compounds containing localized $4d$, $5d$ or $4f$ electrons have recently shown that the quantum spin model on the triangular lattice can be formed by the localized moments~\cite{PhysRevB.86.140405,PhysRevB.94.174410,srep16419,PhysRevLett.115.167203,PhysRevLett.120.087201,CEVALLOS2018154,10.1038/s41535-019-0151-6}. In particular, due to their possible Kramers doublets and spin-orbital coupling, these moments can be treated as $S_{eff}=1/2$ at low temperatures, and the spin-orbital entanglement can induce direction-dependent exchanges, such as the $K$ and $\Gamma$ terms. A typical example is YbMgGaO$_{4}$~\cite{srep16419,PhysRevLett.115.167203}, in which the Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra, but due to the inherent disorder effect there are still controversies about the GS of this material~\cite{srep16419,PhysRevLett.115.167203,PhysRevLett.120.087201,PhysRevB.94.035107,Nature20614,nphys3971,PhysRevLett.117.267202,PhysRevX.8.031028,SciPostPhys.4.1.003,PhysRevB.97.184413}. More recently, an alternative family of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored. The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state~\cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,PhysRevB.100.241116,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}. These triangluar magnets provide suitable platforms to study the interplay of geometric frustation and exchange frustration induced by spin-orbital couplings.

@@

In order to better understand the quantum phases identified by the ED method, we also perform classical Monte Carlo simulations. We begin with paralleling-tempering Monte Carlo~\cite{Hukushima96} on 40 replicas with temperature $T/J$ ranging from $0.001$ to $1.0$. For each replica, we sample it with a combination of heat-bath~\cite{Miyatake84} and over-relaxation method~\cite{Berg} mainly on a $24 \times 24$ triangle lattice with periodic boundary conditions. A whole Monte Carlo step consists of a single heat-bath sweep and subsequent 10 over-relaxation sweeps over the entire lattice. We perform $10^6$ Monte Carlo steps per replica, then, we copy out the spin configuration from the lowest-T replica, and sample it with a combination of zero-temperature heat-bath and over-relaxation method to get the GS. The zero-temperature heat-bath sampling is simply aligning the spins according to their local fields:
\begin{align}
    \bm{S}_{i} = \frac{\bm{h}_{i}^{loc}}{|\bm{h}_{i}^{loc}|} S,
\end{align}
with
\begin{align}
    \bm{h}_{i}^{loc} = \sum_{\langle j \rangle} J \bm{S}_{j} + K {S}^{\gamma}_{j} \hat{e}^{\gamma} + \Gamma (S^{\alpha}_{j} \hat{e}^{\beta} + S^{\beta}_{j} \hat{e}^{\alpha}),
\end{align}
For some competing states, we start from several different initial configurations in order to obtain the correct classical GS.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.95\textwidth]{QuantumGlobalPhaseDiagram.pdf}
    \caption{\label{fig:QuantumPhaseDiagram}(Color online) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total ten phases including three FM phases denoted as FM-A, FM-B and FM-C, three stripe phases denoted as Stripe-A, Stripe-B and Stripe-C, a modulated stripe phase, a 120$^\circ$ N\'{e}el phase, a dual N\'{e}el phase and a possible QSL phase. Phase boundaries are determined by the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ from ED calculations except for that depicted by the dashed line between the modulated stripe and stripe-C phases given by the classical analyses.}
\end{figure*}

The quantum phase diagrams obtained by the ED method for $\Gamma \geq 0$ and $\Gamma \leq 0$ on a $4 \times 6$ cluster with the periodic boundary condition are presented in Fig.~\ref{fig:QuantumPhaseDiagram}, where the phase boundaries are determined by the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ (see Appendix \ref{apx:PhaseBoundary} for details). We find nine magnetically ordered phases and a phase ascribed to be a QSL. The nine ordered magnetic phases consist of three stripe phases (dubbed as stripe-A, strip-B and stripe-C in Fig.~\ref{fig:QuantumPhaseDiagram}), three FM phases (dubbed as FM-A, FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}), one 120$^\circ$ N\'{e}el phase, one dual N\'{e}el phase and one modulated stripe phase. In the followings, we will discuss the details on the natures of these phases and the corresponding phase transitions.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{HKModel.pdf}
    \caption{\label{fig:HKModel}(Color online) Phase diagram in the HK limit ($\Gamma=0$). The double-arrow lines are the representative lines that connect the points exactly related by the FST.}
\end{figure}
Let's first discuss the HK limit for $\Gamma=0$. In accord with the previous study~\cite{KaiLi2015}, we find five quantum phases (see Fig.~\ref{fig:HKModel}). For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$, respectively. So, the phase in the region between $\beta=1.00\pi$ and $1.82\pi$ is identified as FM-A, and that between $\beta=0.23\pi$ and $0.64\pi$ the 120$^\circ$ N\'{e}el state. As introduced in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under the FST, which is in fact a spin-rotation transformation~\cite{PhysRevB.89.014414}. The transformed model has different exchange interactions related to the original ones via Eq.~\eqref{eq:JK} and the mapping angle is given by Eq.~\eqref{eq:angle}. Thus, by virtue of the FST, we can identify other two magnetically ordered phases. Starting from the FM-A phase, it will be transformed to the phase between $\beta=1.00\pi$ and $0.64\pi$ via the angle mapping Eq.~\eqref{eq:angle}. Then, using the spin rotation transformation Eq.~\eqref{eq:FST}, one can identify the phase between $\beta=1.00\pi$ and $0.64\pi$ as a collinear stripe state (denoted as stripe-A). Similarly, the 120$^\circ$ N\'{e}el state is transformed to a noncollinear spiral order (Dual N\'{e}el) in the region from $\beta=1.82\pi$ to $\beta=1.90\pi$. We also note that, as indicated in Fig.~\ref{fig:HKModel}, the transition points $\beta=0.23\pi$ and $0.64\pi$ are indeed mapped to the transition points $\beta=1.90\pi$ and $1.82\pi$ through the FST. However, the transition point $\beta=\pi$ is mapped to itself under the FST, so it the isolated transition point.

@@

For the other two phases with large areas and mainly located in the $J<0$ region of the phase diagram, we show the SSFs of two representative points with $\alpha=0.3\pi, \beta=1.3\pi$ and $\alpha=0.7\pi, \beta=1.65\pi$ in Fig.~\ref{fig:StructureFactors}(f) and (g), respectively. The SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have FM orders and they are denoted with FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}. We note that there are two special points with $\Gamma=\pm1$ ($J=K=0$) in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}. Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform an analysis based on the ``basin-hopping" global optimization and classical Monte Carlo methods. For $\Gamma=+1$, apart from the FM GS with the spin orientation lying in the lattice plane, we also found disordered states having the same energy as the FM state (see Appendix~\ref{apx:DegeneratedStates} for details). For $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, there are also several noncollinear magnetic orders energetically degenerate with the FM state (see Appendix~\ref{apx:DegeneratedStates} for details). However, according to our ED calculations, for the quantum model, quantum fluctuations select the FM ordered states as the GS out of the degenerate manifolds of classical states. This selection of states among the degenerate classical GSs is the so called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical GS configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{StructureFactors.pdf}
    \caption{\label{fig:StructureFactors}(Color online) SSFs from the ED calculations for representative interaction parameters in different phases: (a) stripe-B, (b) and (c) stripe-A, (d) stripe-C, (e) modulated stripe, (f) FM-B, (g) FM-C, (h) QSL. The green dashed lines mark the first BZ of the triangular lattice. (i) Characteristic wave vectors for the FM and stripe phases. See Appendix~\ref{apx:SSF} for the SSFs of the 120$^\circ$ N\'{e}el phase, dual N\'{e}el phase and pure $\Gamma$ models.}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{ModulatedStripe.pdf}
    \caption{\label{fig:ModulatedStripe}(Color online) (a) Spin configuration obtained from basin-hopping optimization for $\alpha=0.3\pi$, $\beta=0.5\pi$ in a $12 \times 12$ cluster. (b) SSF corresponding to the spin configuration shown in (a). (c) Spin configuration obtained from the classical Monte Carlo calculations in a $24 \times 24$ cluster.}
\end{figure}

@@

In order to confirm the consistency between the above classical analyses and the ED results, we use the spin coherent state to extract the moment directions of these FM phases from our ED cluster GSs~\cite{PhysRevB.94.064435}. Since the cluster spin coherent state defined in Eq.~(\ref{eq:Spin-1/2CoherentState}) is captured only by a single pair of $(\theta, \phi)$ for the collinear states, it is easy to determine the directions of the FM orders by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$. As shown in Fig.~\ref{fig:Proabilities}(a), for the FM-B phase, the peaks of the probability form a ring, indicating that the moment is constrained to a plane with all directions degenerate. To compare with the classical results, we plot the classical magnetic moment directions with the green dashed line in Fig.~\ref{fig:Proabilities}(a), and find that the probability centers on the classical magnetic moment directions. For the FM-C phase, the probability map is clearly peaked at specific directions, which are also consistent with the classical results marked by the green solid circle in Fig. \ref{fig:Proabilities}(b). Moreover, the large overlaps between the exact cluster GSs and FM cluster spin coherent states again provide solid evidences that the ED results are consistent with the classical analyses.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{Probabilities.pdf}
    \caption{\label{fig:Proabilities}(Color online) Maps of the probabilities of the cluster spin coherent states given by Eq.~\eqref{eq:Spin-1/2CoherentState} in exact cluster GS for (a) FM-B, (b) FM-C, (c) stripe-A and (d) stripe-C phases. The radial and polar coordinate give the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b). The green dashed line and solid circles mark the ordered moment directions for the classical states. Note that the GSs are two-fold degenerate for the FM-C phase, and six-fold degenerate for the stripe-A and stripe-C phases, so the total probabilities for all of these phases are approximate to $1$. }
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{Spectrum.pdf}
    \caption{\label{fig:Spectrum}(Color online) DSF $A(\bm{k}, \omega)$ for $\alpha=0.05\pi,\beta=0.1\pi$ in the QSL phase. The path $\tilde{M}-\tilde{\Gamma}-\tilde{M}-\tilde{\Gamma}$ is shown in Fig.~\ref{fig:StructureFactors}(i).}
\end{figure}

@@

\begin{acknowledgments}
This work was supported by the National Natural Science Foundation of China (Grants No. 11674158, No. 11774152 and No. 11774300) and National Key Projects for Research and Development of China (Grant No. 2016YFA0300401).
\end{acknowledgments}

@@

\section{\label{apx:PhaseBoundary}Phase boundaries in the quantum phase diagram}

As mentioned in the main text, the phase boundaries are determined by the locations of singularities in $-\partial^{2} E_{2} / \partial \alpha^{2}$ and $-\partial^{2} E_{0} / \partial \beta^{2}$ based on the ED calculations. Some representative curves are shown in Fig.~\ref{fig:SecondDerivatives}. In Fig.~\ref{fig:SecondDerivatives}(a) for $\alpha=0.05\pi$, the second derivative of $E_0$ versus $\beta$ has two peaks located at $\beta=-0.01\pi$ and $\beta=0.81\pi$, which are the phase boundaries between the FM-B and QSL phases. As we increase $\alpha$ to $0.3\pi$, there are three singularities in the second derivatives (see Fig.~\ref{fig:SecondDerivatives}(b)). The small peak at $\beta=0.62\pi$ indicates the phase transition from modulated stripe to stripe-A, while the other two sharp peaks at $\beta=0.94\pi$ and $\beta=1.87\pi$ originate from the phase transitions from stripe-A to FM-B and from FM-B to stripe-C, respectively. Fig.~\ref{fig:SecondDerivatives}(c) shows the case for $\alpha=0.75\pi$, where the two peaks located at $\beta=0.87\pi$ and $\beta=1.89\pi$ signify the phase transitions between stripe-A and FM-C. On the other hand, we can also fix $\beta$ to detect the phase transitions with varying $\alpha$ and the corresponding results are shown in Figs.~\ref{fig:SecondDerivatives}(d)-(f). In Fig.~\ref{fig:SecondDerivatives}(d), $\beta$ equals to $0$, the first two sharp peaks at $\alpha=0.045\pi$ and $\alpha=0.097\pi$ reveal the phase transitions from FM-B to QSL and further to stripe-C. The peak at about $\alpha=0.5\pi$ is due to the phase transition from stripe-C to stripe-A. The last singularity at $\alpha=0.93\pi$ marks the phase boundary between stripe-A and FM-C. In Fig.~\ref{fig:SecondDerivatives}(e), we show the phase transition between modulated stripe and 120$^\circ$ N\'{e}el as well as the phase transition from 120$^\circ$ N\'{e}el to stripe-A. Here, $\beta$ is fixed to $0.5\pi$, and the transitions occur at $\alpha=0.32\pi$ and $\alpha=0.62\pi$, respectively. Last but not least, we show there are phase transitions between these different FM phases. In Fig.~\ref{fig:SecondDerivatives}(f) where $\beta=1.5\pi$, the sharp peak at $\alpha=0.5\pi$ shows that the FM-A phase for the HK model is a phase-transition boundary, infinitesimal $\Gamma$ interaction will cause phase transitions to other FM phases which have different moment directions from the FM-A phase.

>>>>

\documentclass[aps,prb,reprint,amsfonts,amsmath,amssymb,showpacs,groupedaddress,superscriptaddress]{revtex4-1}
\usepackage{bm}
\usepackage{color}
\usepackage{graphicx}
\usepackage[colorlinks,urlcolor=blue,linkcolor=blue,anchorcolor=blue,citecolor=blue,bookmarks]{hyperref}
\usepackage{changes}
    \definechangesauthor[name={Shi Wang}, color=red]{swang}
    \setauthormarkup{}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/ModelDefinition.pdf}
    \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron. (b) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron. The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame. (c) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively. The different colors of the lattice sites label the four sublattices realizing the four sublattice transformation ( see main text for details).}
\end{figure}
In fact, magnetic ions located at the center of edge-sharing octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}. On the experimental side, studies on several classes of  compounds containing localized $4d$, $5d$ or $4f$ electrons have recently shown that the quantum spin model on the triangular lattice can be formed by the localized moments~\cite{PhysRevB.86.140405,PhysRevB.94.174410,srep16419,PhysRevLett.115.167203,PhysRevLett.120.087201,CEVALLOS2018154,10.1038/s41535-019-0151-6}. In particular, due to their possible Kramers doublets and spin-orbital coupling, these moments can be treated as $S_{eff}=1/2$ at low temperatures, and the spin-orbital entanglement can induce direction-dependent exchanges, such as the $K$ and $\Gamma$ terms. A typical example is YbMgGaO$_{4}$~\cite{srep16419,PhysRevLett.115.167203}, in which the Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra, but due to the inherent disorder effect there are still controversies about the GS of this material~\cite{srep16419,PhysRevLett.115.167203,PhysRevLett.120.087201,PhysRevB.94.035107,Nature20614,nphys3971,PhysRevLett.117.267202,PhysRevX.8.031028,SciPostPhys.4.1.003,PhysRevB.97.184413}. More recently, an alternative family of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored. The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state~\cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,PhysRevB.100.241116,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}. These triangluar magnets provide suitable platforms to study the interplay of geometric frustation and exchange frustration induced by spin-orbital couplings.

@@

In order to better understand the quantum phases identified by the ED method, we also perform classical Monte Carlo simulations. We begin with paralleling-tempering Monte Carlo~\cite{Hukushima96} on 40 replicas with temperature $T/J$ ranging from $0.001$ to $1.0$. For each replica, we sample it with a combination of heat-bath~\cite{Miyatake84} and over-relaxation method~\cite{Berg} mainly on a $24 \times 24$ triangle lattice with periodic boundary conditions. A whole Monte Carlo step consists of a single heat-bath sweep and subsequent 10 over-relaxation sweeps over the entire lattice. We perform $10^6$ Monte Carlo steps per replica, then, we copy out the spin configuration from the lowest-T replica, and sample it with a combination of zero-temperature heat-bath and over-relaxation method to get the GS. The zero-temperature heat-bath sampling is simply aligning the spins according to their local fields:
\begin{align}
    \vec{S}_{i} = \frac{\vec{h}_{i}^{loc}}{|\vec{h}_{i}^{loc}|} S,
\end{align}
with
\begin{align}
    \vec{h}_{i}^{loc} = \sum_{\langle j \rangle} J \vec{S}_{j} + K {S}^{\gamma}_{j} \hat{e}^{\gamma} + \Gamma (S^{\alpha}_{j} \hat{e}^{\beta} + S^{\beta}_{j} \hat{e}^{\alpha}),
\end{align}
\added[swang]{
    and the over-relaxation sampling is just mirror reflection of a spin with respect to the local field:
    \begin{eqnarray}
        \vec{S}_i^{new} & = &\frac{2 (\vec{S}_i^{old} \cdot \vec{h}_i^{loc}) \vec{h}_i^{loc}}{|\vec{h}_i^{loc}|^2}-\vec{S}_i^{old}.
    \end{eqnarray}
}
For some competing states, we start from several different initial configurations in order to obtain the correct classical GS.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.95\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
    \caption{\label{fig:QuantumPhaseDiagram}(Color online) \replaced[swang]{Zero-temperature global}{Global} phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total ten phases including three FM phases denoted as FM-A, FM-B and FM-C, three stripe phases denoted as Stripe-A, Stripe-B and Stripe-C, a modulated stripe phase, a 120$^\circ$ N\'{e}el phase, a dual N\'{e}el phase and a possible QSL phase. Phase boundaries are determined by the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ from ED calculations except for that depicted by the dashed line between the modulated stripe and stripe-C phases given by the classical analyses.}
\end{figure*}

The \added[swang]{zero-temperature} quantum phase diagrams obtained by the ED method for $\Gamma \geq 0$ and $\Gamma \leq 0$ on a $4 \times 6$ cluster with the periodic boundary condition are presented in Fig.~\ref{fig:QuantumPhaseDiagram}, where the phase boundaries are determined by the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ (see Appendix \ref{apx:PhaseBoundary} for details). We find nine magnetically ordered phases and a phase ascribed to be a QSL. The nine ordered magnetic phases consist of three stripe phases (dubbed as stripe-A, strip-B and stripe-C in Fig.~\ref{fig:QuantumPhaseDiagram}), three FM phases (dubbed as FM-A, FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}), one 120$^\circ$ N\'{e}el phase, one dual N\'{e}el phase and one modulated stripe phase. In the followings, we will discuss the details on the natures of these phases and the corresponding phase transitions.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/HKModel.pdf}
    \caption{\label{fig:HKModel}(Color online) Phase diagram in the HK limit ($\Gamma=0$). The double-arrow lines are the representative lines that connect the points exactly related by the FST.}
\end{figure}
Let's first discuss the HK limit for $\Gamma=0$. In accord with the previous study~\cite{KaiLi2015}, we find five quantum phases (see Fig.~\ref{fig:HKModel}). For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$, respectively. So, the phase in the region between $\beta=1.00\pi$ and $1.82\pi$ is identified as FM-A, and that between $\beta=0.23\pi$ and $0.64\pi$ the 120$^\circ$ N\'{e}el state. As introduced in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under the FST, which is in fact a spin-rotation transformation~\cite{PhysRevB.89.014414}. The transformed model has different exchange interactions related to the original ones via Eq.~\eqref{eq:JK} and the mapping angle is given by Eq.~\eqref{eq:angle}. Thus, by virtue of the FST, we can identify other two magnetically ordered phases. Starting from the FM-A phase, it will be transformed to the phase between $\beta=1.00\pi$ and $0.64\pi$ via the angle mapping Eq.~\eqref{eq:angle}. Then, using the spin rotation transformation Eq.~\eqref{eq:FST}, one can identify the phase between $\beta=1.00\pi$ and $0.64\pi$ as a collinear stripe state (denoted as stripe-A). Similarly, the 120$^\circ$ N\'{e}el state is transformed to a noncollinear spiral order (Dual N\'{e}el) in the region from $\beta=1.82\pi$ to $\beta=1.90\pi$. We also note that, as indicated in Fig.~\ref{fig:HKModel}, the transition points $\beta=0.23\pi$ and $0.64\pi$ are indeed mapped to the transition points $\beta=1.90\pi$ and $1.82\pi$ through the FST. However, the transition point $\beta=\pi$ is mapped to itself under the FST, so it the isolated transition point.

@@

For the other two phases with large areas and mainly located in the $J<0$ region of the phase diagram, we show the SSFs of two representative points with $\alpha=0.3\pi, \beta=1.3\pi$ and $\alpha=0.7\pi, \beta=1.65\pi$ in Fig.~\ref{fig:StructureFactors}(f) and (g), respectively. The SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have FM orders and they are denoted with FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}. We note that there are two special points with $\Gamma=\pm1$ ($J=K=0$) in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}. Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform an analysis based on the ``basin-hopping" global optimization and classical Monte Carlo methods. For $\Gamma=+1$, apart from the FM GS with the spin orientation lying in the lattice plane, we also found disordered states having the same energy as the FM state (see Appendix~\ref{apx:DegeneratedStates} for details). For $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, there are also several noncollinear magnetic orders energetically degenerate with the FM state (see Appendix~\ref{apx:DegeneratedStates} for details). However, according to our ED calculations, for the quantum model, quantum fluctuations select the FM ordered states as the GS out of the degenerate manifolds of classical states. This selection of states among the degenerate classical GSs is the so called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical GS configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/StructureFactors.pdf}
    \caption{\label{fig:StructureFactors}(Color online) SSFs from the ED calculations for representative interaction parameters in different phases: (a) stripe-B, (b) and (c) stripe-A, (d) stripe-C, (e) modulated stripe, (f) FM-B, (g) FM-C, (h) QSL. The green dashed lines mark the first BZ of the triangular lattice. (i) Characteristic wave vectors for the \replaced[swang]{FM (blue circle), stripe (orange square), 120$^\circ$ N\'{e}el (red up-triangle) and dual N\'{e}el (purple down-triangle)}{FM and stripe} phases. See Appendix~\ref{apx:SSF} for the SSFs of the 120$^\circ$ N\'{e}el phase, dual N\'{e}el phase and pure $\Gamma$ models.}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{fig/ModulatedStripe.pdf}
    \caption{\label{fig:ModulatedStripe}(Color online) (a) Spin configuration obtained from basin-hopping optimization for $\alpha=0.3\pi$, $\beta=0.5\pi$ in a $12 \times 12$ cluster. (b) SSF corresponding to the spin configuration shown in (a). (c) Spin configuration obtained from the classical Monte Carlo calculations in a $24 \times 24$ cluster.}
\end{figure}

@@

In order to confirm the consistency between the above classical analyses and the ED results, we use the spin coherent state to extract the moment directions of these FM phases from our ED cluster GSs~\cite{PhysRevB.94.064435}. Since the cluster spin coherent state defined in Eq.~(\ref{eq:Spin-1/2CoherentState}) is captured only by a single pair of $(\theta, \phi)$ for the collinear states, it is easy to determine the directions of the FM orders by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$. As shown in Fig.~\ref{fig:Proabilities}(a), for the FM-B phase, the peaks of the probability form a ring, indicating that the moment is constrained to a plane with all directions degenerate. To compare with the classical results, we plot the classical magnetic moment directions with the green dashed line in Fig.~\ref{fig:Proabilities}(a), and find that the probability centers on the classical magnetic moment directions. For the FM-C phase, the probability map is clearly peaked at specific directions, which are also consistent with the classical results marked by the green solid circle in Fig. \ref{fig:Proabilities}(b). Moreover, the large overlaps between the exact cluster GSs and FM cluster spin coherent states again provide solid evidences that the ED results are consistent with the classical analyses.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/Probabilities.pdf}
    \caption{\label{fig:Proabilities}(Color online) Maps of the probabilities of the cluster spin coherent states given by Eq.~\eqref{eq:Spin-1/2CoherentState} in exact cluster GS for (a) FM-B, (b) FM-C, (c) stripe-A and (d) stripe-C phases. The radial and polar coordinate give the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b). The green dashed line and solid circles mark the ordered moment directions for the classical states. Note that the GSs are two-fold degenerate for the FM-C phase, and six-fold degenerate for the stripe-A and stripe-C phases, so the total probabilities for all of these phases are approximate to $1$. }
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/Spectrum.pdf}
    \caption{\label{fig:Spectrum}(Color online) DSF $A(\bm{k}, \omega)$ for $\alpha=0.05\pi,\beta=0.1\pi$ in the QSL phase. The path $\tilde{M}-\tilde{\Gamma}-\tilde{M}-\tilde{\Gamma}$ is shown in Fig.~\ref{fig:StructureFactors}(i).}
\end{figure}

@@

\begin{acknowledgments}
This work was supported by the National Natural Science Foundation of China (Grants No. 11674158, No. 11774152\replaced[swang]{, No. 11774300 and No. 12004191}{ and No. 11774300})\replaced[swang]{,}{ and} National Key Projects for Research and Development of China (Grant No. 2016YFA0300401) \added[swang]{and Natural Science Foundation of Jiangsu Province, China (Grant No. BK20200738)}.
\end{acknowledgments}

@@

\section{\label{apx:PhaseBoundary}Phase boundaries in the \added[swang]{zero-temperature} quantum phase diagram}

As mentioned in the main text, the phase boundaries are determined by the locations of singularities in $-\partial^{2} E_{0} / \partial \alpha^{2}$ and $-\partial^{2} E_{0} / \partial \beta^{2}$ based on the ED calculations. Some representative curves are shown in Fig.~\ref{fig:SecondDerivatives46}. In Fig.~\ref{fig:SecondDerivatives46}(a) for $\alpha=0.05\pi$, the second derivative of $E_0$ versus $\beta$ has two peaks located at $\beta=-0.01\pi$ and $\beta=0.81\pi$, which are the phase boundaries between the FM-B and QSL phases. As we increase $\alpha$ to $0.3\pi$, there are three singularities in the second derivatives (see Fig.~\ref{fig:SecondDerivatives46}(b)). The small peak at $\beta=0.62\pi$ indicates the phase transition from modulated stripe to stripe-A, while the other two sharp peaks at $\beta=0.94\pi$ and $\beta=1.87\pi$ originate from the phase transitions from stripe-A to FM-B and from FM-B to stripe-C, respectively. Fig.~\ref{fig:SecondDerivatives46}(c) shows the case for $\alpha=0.75\pi$, where the two peaks located at $\beta=0.87\pi$ and $\beta=1.89\pi$ signify the phase transitions between stripe-A and FM-C. On the other hand, we can also fix $\beta$ to detect the phase transitions with varying $\alpha$ and the corresponding results are shown in Figs.~\ref{fig:SecondDerivatives46}(d)-(f). In Fig.~\ref{fig:SecondDerivatives46}(d), $\beta$ equals to $0$, the first two sharp peaks at $\alpha=0.045\pi$ and $\alpha=0.097\pi$ reveal the phase transitions from FM-B to QSL and further to stripe-C. The peak at about $\alpha=0.5\pi$ is due to the phase transition from stripe-C to stripe-A. The last singularity at $\alpha=0.93\pi$ marks the phase boundary between stripe-A and FM-C. In Fig.~\ref{fig:SecondDerivatives46}(e), we show the phase transition between modulated stripe and 120$^\circ$ N\'{e}el as well as the phase transition from 120$^\circ$ N\'{e}el to stripe-A. Here, $\beta$ is fixed to $0.5\pi$, and the transitions occur at $\alpha=0.32\pi$ and $\alpha=0.62\pi$, respectively. Last but not least, we show there are phase transitions between these different FM phases. In Fig.~\ref{fig:SecondDerivatives46}(f) where $\beta=1.5\pi$, the sharp peak at $\alpha=0.5\pi$ shows that the FM-A phase for the HK model is a phase-transition boundary, infinitesimal $\Gamma$ interaction will cause phase transitions to other FM phases which have different moment directions from the FM-A phase.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/SecondDerivatives46.pdf}
    \caption{\label{fig:SecondDerivatives46} (Color online) GS energies and their second derivatives versus $\alpha$ or $\beta$ for six representative paths in the phase diagram. \added[swang]{The ED calculations are performed on a $4 \times 6$ cluster with periodic boundary condition.} The blue lines are the GS energies and the red lines are the second derivatives. In (a)-(c) $\alpha$ is fixed to $0.05\pi$, $0.3\pi$ and $0.75\pi$, respectively. In (d)-(f), $\beta$ is fixed to $0$, $0.5\pi$ and $1.5\pi$, respectively.}
\end{figure}
